---
title: "Explore Fish Diversity 2017-2018: Figures"
author: "Sean Kinard"
date: "2023-02-09"
output: 
  pdf_document: 
    fig_caption: yes
editor_options: 
  markdown: 
    wrap: 72
---

```{r R Setup, include = F, echo=F, message=F}
#------------------------------------------------------------------------------
# Setup: Clear Global Environment & load tools for analytical scripts
#------------------------------------------------------------------------------

# Clean Workspace
rm(list=ls())

# Data Tools
library(tidyverse)
library(lubridate)
library(BiodiversityR)
library(car)

# Plot Tools
library(paletteer)
library(ggsignif)
library(patchwork)
library(knitr)
library("ggpmisc")
library(ggrepel)
library(kableExtra)
library(ggpubr)
library(ggbiplot)

site_order <- c("TR", "SF", "AR", "MR", "PD", "PL", "GC", "WM", "EM")

my_colors <- c('#F5191CFF', '#E78200FF', '#E8A117FF',
               '#EABB22FF', '#CBC988FF', '#9FC095FF',
               '#6BB699FF', '#3DAAA6FF', '#3B99B1FF')

#------------------------------------------------------------------------------
# End setup
```

```{r Analyses, include=F, echo=F, message=F}
#------------------------------------------------------------------------------
# Load Scripts to Populate Global Environment with Figures and Tables
#------------------------------------------------------------------------------
setwd("/home/kinard/Documents/Research/Dissertation/02_Resilience")

source('R_Scripts/027_diversity_figures.R')

#------------------------------------------------------------------------------
# End Analyses
```

\newpage

## Figure 1 - Diversity vs Rainfall: Boxplot

```{r Figure 1, echo=F, echo=F, message=F, warning=FALSE, fig.height=8, fig.width=6, fig.align = 'center'}
div_vs_site
```

Figure 1. Diversity of fish (species richness, Shannon-Wiener Index, and Simpon's Index) at each sampling location from from 2017, 2018, and 2020. 2017 contains 3 months following hurricane Harvey, 2018
contains monthly samples from January through October, and 2020 contains
quarterly sampling.

\newpage

## Figure 2 - Diversity vs Diatom Concentration

```{r Figure 2, echo=F, echo=F, message=F, warning=FALSE, fig.height=8, fig.width=6, fig.align = 'center'}
div_vs_diatoms
```

Figure 2. Community diversity versus diatom chlorophyll concentrations for 2017, 2018, and 2020. To aid visualization, the horizontal axis is log transformed.

\newpage

## Figure 3 - Diversity vs 2-Week Maximum Discharge

```{r Figure 3, echo=F, echo=F, message=F, warning=FALSE, fig.height=8, fig.width=6, fig.align = 'center'}
div_vs_qmax
```

Figure 3. Community diversity versus maximum discharge in the two weeks prior to sampling for 2017, 2018, and 2020. To aid visualization, the horizontal axis is log transformed.

\newpage

## Figure 4 - Diversity vs Nitrate Concentrations

```{r Figure 4, echo=F, echo=F, message=F, warning=FALSE, fig.height=8, fig.width=6, fig.align = 'center'}
div_vs_nitrate
```

Figure 4. Community diversity versus nitrate concentrations for 2017, 2018, and 2020. Both axes are log transformed.

\newpage

## Figure 5 - Diversity vs Time: Community 

```{r Figure 5, echo=F, echo=F, message=F, warning=FALSE, fig.height=8, fig.width=6, fig.align = 'center'}
div_vs_time
```

Figure 5. Community diversity versus day of the year for 2017, 2018, and 2020. Densities and smoothed regression curves are are colored by annual rainfall and a region-wide (all sites) smoothed regression is in dark grey.

\newpage

## Figure 6 - Diversity vs Rainfall (Annually): Regression

```{r Figure 6, echo=F, echo=F, message=F, warning=FALSE, fig.height=8, fig.width=6, fig.align = 'center'}
div_vs_rainfall_annual
```

Figure 6. Community diversity versus annual rainfall for 2017, 2018, and 2020.

\newpage

## Figure 7 - Richness vs Rainfall (Quarterly): Regression

```{r Figure 7, echo=F, echo=F, message=F, warning=FALSE, fig.height=8, fig.width=6, fig.align = 'center'}
richness_vs_rainfall_quarterly
```

Figure 7. Species richness of fish communities versus annual rainfall for 2017, 2018, and 2020, divided by quarter of the year.

\newpage

## Figure 8 - Shannon vs Rainfall (Quarterly): Regression

```{r Figure 8, echo=F, echo=F, message=F, warning=FALSE, fig.height=8, fig.width=6, fig.align = 'center'}
shannon_vs_rainfall_quarterly
```

Figure 8. Shannon diversity of fish communities versus annual rainfall for 2017, 2018, and 2020, divided by quarter of the year.
