---
title: "Fish Counts and Lengths"
author: "Sean Kinard"
date: "2023-03-03"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
---
```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_dark(base_color = "cornsilk1")
```


```{r setup, include=FALSE}
setwd("/home/kinard/Documents/Research/Dissertation/02_Resilience")

library(tidyverse) # all tidyverse packages
library(lubridate) # date managment
library(vegan)
library(ggdark)
library(vegan)
library(BiodiversityR)
library(car)
library(paletteer)
library(ggsignif)
library(patchwork)
library(knitr)
library("ggpmisc")
library(ggrepel)
library(kableExtra)
library(ggpubr)
library(ggbiplot)

# load data
source('R_Scripts/000_d_dataframes.R')
source('R_Scripts/000_biological_scales_comparison.R')
source('R_Scripts/065_response_v2.R')
```

# Taxonomic Families
- Poeciliidae
    - G. affinis, P. latipinna

- Centrarchidae
    - L. auritus, L. cyanellus, L. gulosus, L. humilis, L. macrochirus, L. megalotis, L. microlophus, L. miniatus
    - M. salmoides, P. annularis, P. nigromaculatus

- Ictaluridae
    - A. melas, A. natalis, I. punctatus, N. gyrinus, P. olivaris

- Lepisosteidae
    - L. oculatus 

- Leuciscidae
    - C. lutrensis, C. venusta, N. texanus, P. vigilax

- Cichlidae
    - H. cyanoguttatum, O. aureus

- Cyprinidontidae
    - C. variegatus
    
---
# Plot Description
- For a group of comparison:
    - Count(red) and Size (Yellow) are plotted against time
    - Time is blocked by year
    - Count and Length variables are scaled within group of comparison and within sampling location
    - localized smoother improves visualization of trends through time
    
- Stable Count (red) and elevated size (yellow) implicates growth
- high Count (red) and depreciated size (yellow implicates breeding events
- parallel upward trends implicate immigration of larger fish
- parallel downward trends implicate loss or emigration of larger fish

---
# Poeciliidae
- Includes : G. affinis, P. latipinna
- Post-hurricane peak in 2017
- Seasonal peak in 2nd Quarter of 2020
- 

---
```{r , echo=F, echo=F, message=F, warning=F, fig.dim=c(18,14)}
setwd("/home/kinard/Documents/Research/Dissertation/02_Resilience")
group_scale_plot('family', 'Poeciliidae')
```
Seasonal peak in the 2nd Quarter of 2020

---
```{r , echo=F, echo=F, message=F, warning=F, fig.dim=c(18,14)}
setwd("/home/kinard/Documents/Research/Dissertation/02_Resilience")
group_scale_plot('family', 'Centrarchidae')
```

---
```{r , echo=F, echo=F, message=F, warning=F, fig.dim=c(18,14)}
setwd("/home/kinard/Documents/Research/Dissertation/02_Resilience")
group_scale_plot('family', 'Ictaluridae')
```

---
```{r , echo=F, echo=F, message=F, warning=F, fig.dim=c(18,14)}
setwd("/home/kinard/Documents/Research/Dissertation/02_Resilience")
group_scale_plot('family', 'Lepisosteidae')
```

---
```{r , echo=F, echo=F, message=F, warning=F, fig.dim=c(18,14)}
setwd("/home/kinard/Documents/Research/Dissertation/02_Resilience")
group_scale_plot('family', 'Leuciscidae')
```

---
```{r , echo=F, echo=F, message=F, warning=F, fig.dim=c(18,14)}
setwd("/home/kinard/Documents/Research/Dissertation/02_Resilience")
group_scale_plot('family', 'Cichlidae')
```

---
```{r , echo=F, echo=F, message=F, warning=F, fig.dim=c(18,14)}
setwd("/home/kinard/Documents/Research/Dissertation/02_Resilience")
group_scale_plot('family', 'Cyprinodontidae')
```

---
# Taxonomic Species

- L. macrochirus (Bluegill Sunfish)
- L. gulosus (Warmouth Sunfish)
- L. cyanellus (Green Sunfish)
- H. cyanoguttatum (Rio Grande Cichlid)
- G. affinis (Western Mosquitofish)
- P. latipinna (Sailfin Molly)
- C. variegatus (Sheepshead Minnow)
- P. vigilax (Bullnose Minnow)

---

```{r , echo=F, echo=F, message=F, warning=F, fig.dim=c(18,14)}
setwd("/home/kinard/Documents/Research/Dissertation/02_Resilience")
group_scale_plot('lowest_taxon', 'L. macrochirus')
```

---

```{r , echo=F, echo=F, message=F, warning=F, fig.dim=c(18,14)}
setwd("/home/kinard/Documents/Research/Dissertation/02_Resilience")
group_scale_plot('lowest_taxon', 'L. megalotis')
```

---

```{r , echo=F, echo=F, message=F, warning=F, fig.dim=c(18,14)}
setwd("/home/kinard/Documents/Research/Dissertation/02_Resilience")
group_scale_plot('lowest_taxon', 'L. gulosus')
```

---

```{r , echo=F, echo=F, message=F, warning=F, fig.dim=c(18,14)}
setwd("/home/kinard/Documents/Research/Dissertation/02_Resilience")
group_scale_plot('lowest_taxon', 'L. cyanellus')
```

---

```{r , echo=F, echo=F, message=F, warning=F, fig.dim=c(18,14)}
setwd("/home/kinard/Documents/Research/Dissertation/02_Resilience")
group_scale_plot('lowest_taxon', 'H. cyanoguttatum')
```

---

```{r , echo=F, echo=F, message=F, warning=F, fig.dim=c(18,14)}
setwd("/home/kinard/Documents/Research/Dissertation/02_Resilience")
group_scale_plot('lowest_taxon', 'P. latipinna')
```

---

```{r , echo=F, echo=F, message=F, warning=F, fig.dim=c(18,14)}
setwd("/home/kinard/Documents/Research/Dissertation/02_Resilience")
group_scale_plot('lowest_taxon', 'G. affinis')
```

---

```{r , echo=F, echo=F, message=F, warning=F, fig.dim=c(18,14)}
setwd("/home/kinard/Documents/Research/Dissertation/02_Resilience")
 group_scale_plot('lowest_taxon', 'C. variegatus')
```

---

```{r , echo=F, echo=F, message=F, warning=F, fig.dim=c(18,14)}
setwd("/home/kinard/Documents/Research/Dissertation/02_Resilience")
group_scale_plot('lowest_taxon', 'P. vigilax')
```

---

# Trophic Category

- Herbivore
    - B. patronus, C. variegatus, D. cepedianum, O. aureus, P. latipinna
- Omnivore
    - everything else
- Piscivore
    - A. melas, A. mitchilli, A. rostrata, G. dormitor, I. punctatus,
    L. cyanellus, L. megalotis, L. microlophus, L. oculatus, M. salmoides, P. annularis, P. nigromaculatus, P. olivaris

---

```{r , echo=F, echo=F, message=F, warning=F, fig.dim=c(18,14)}
setwd("/home/kinard/Documents/Research/Dissertation/02_Resilience")
group_scale_plot('trophic_category', 'Herbivore')
```

---

```{r , echo=F, echo=F, message=F, warning=F, fig.dim=c(18,14)}
setwd("/home/kinard/Documents/Research/Dissertation/02_Resilience")
group_scale_plot('trophic_category', 'Omnivore')
```

---

```{r , echo=F, echo=F, message=F, warning=F, fig.dim=c(18,14)}
setwd("/home/kinard/Documents/Research/Dissertation/02_Resilience")
group_scale_plot('trophic_category', 'Piscivore')
```

